Twists of supersymmetric gauge theories

### 2019-08-18 paper.tex
Comments based on conversations with Pavel earlier

\begin{dfn}
A {\bf free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{dfn}

We call $\cE$ the {\bf space of BV fields}.
\chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}

\begin{dfn}
A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[
I \in \oloc^+(\cE)
\]
of cohomological degree zero satisfying the classical master equation 
\[
Q I + \frac{1}{2} \{I,I\} = 0 .
\]
\end{dfn}

Given a classical field theory $(E, Q, \omega, I)$ we denote by
\[S_{BV} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
the BV action of the theory.

@@

\begin{dfn}
A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
\[
F\colon E \to E'
\]
that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
\end{dfn}

@@

\begin{dfn} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
\[
F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{dfn}

@@

\begin{dfn} \label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{dfn}

@@

Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{BV}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
for every $k\geq 0$.

@@

\begin{dfn}
Let $(E, Q, \omega, I)$ be a classical field theory on $M$. The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
\[
\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
\]
\end{dfn}

@@

\begin{dfn}
A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{BRST} S_{BRST} = 0,\]
where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
\end{dfn}

@@

The interacting theory is constructed as follows. First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$. These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
\] 
which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I_{BV} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
\]

@@

\begin{dfn}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The {\bf generalized BF theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

@@

\item The BRST action is $S_{BRST} = 0$.
\end{itemize}
\end{dfn}

@@

\begin{dfn}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The {\bf generalized Chern--Simons theory} is the following classical BV theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

@@

\item The interaction term is
\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
\end{itemize}
\label{def:generalizedBF}
\end{dfn}

@@

\begin{dfn}
A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
\end{dfn}

@@

\begin{dfn}
Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$. The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
\end{dfn}

@@

\begin{dfn}
A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
\end{dfn}

@@

@@

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
 &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &=
\end{align*}
Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
\chris{What about that $[Q_1,Q_2]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q_1,Q_2]$.}
\end{proof}

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
 &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
 &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
\end{align*}
where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
\begin{align*}
\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
\end{align*}
since \chris{The equality of the first terms looks right when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
I don't see that here -- is that true?  I might be missing something.}.

@@

\begin{dfn}
A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
\end{dfn}

@@

\begin{dfn}
A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
\end{dfn}

@@

\begin{dfn}
Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{dfn}

@@

In 8 dimensions, there are 3 classes of non-equivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Pure spinors, with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are holomorphic.  They are stabilized by $\SU(4)$.  Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
 \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are topological.  They are stabilized by $\Spin(7) \sub \SO(8)$.  Again, twists by such supercharges can be made $\ZZ$-graded.
 \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

\begin{dfn}
Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
For any open set $U \subset M$, define the following notations:
\begin{itemize}
\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
\end{itemize}
\end{dfn}

@@

\begin{dfn}\label{dfn: fnl}
Let $E$ be a vector bundle on $M$ and $U \subset M$.
The {\bf completed algebra of functions} on $\cE(U)$ is
\[
\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
\]
On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
\end{dfn}

@@

\begin{dfn} 
We use the following notations and naming conventions for sheaves on $\Mfld$:
\begin{itemize}
\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
\[
\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
\]
for every smooth manifold $X$, which is required to be natural under pullbacks:
\[
f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
\]
for every smooth map $f : X \to Y$. 
A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
\end{itemize}
\end{dfn}

@@

\begin{dfn}
Suppose $V,W$ are cochain complexes in convenient vector spaces. 
A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
\[
dif_c (f) : dif_c(V) \to dif_c(W)
\]
is a quasi-isomorphism of differentiable vector spaces.
\end{dfn}

>>>>

\begin{definition}
A {\bf free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
\begin{definition}
The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
\end{definition}

\begin{definition}
A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[I \in \oloc^+(\cE)\]
of cohomological degree zero satisfying the classical master equation 
\[Q I + \frac{1}{2} \{I,I\} = 0 .\]
\end{definition}

Given a classical field theory $(E, Q, \omega, I)$ we denote by
\[S_{\mr{BV}} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
the BV action of the theory.

@@

\begin{definition}
A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
\[
F\colon E \to E'
\]
that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
\end{definition}

@@

\begin{definition} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
\[
F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{definition}

@@

\subsection{Symmetries in the Classical BV Formalism}

\chris{The idea, and a description of the kind of infinitesimal symmetries we're talking about (maybe just by a super Lie algebra in this paper, although we allow $L_\infty$ actions).  More generally we might consider the action of general local $L_\infty$ algebras.}

\begin{definition} \label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{definition}

@@

Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{\mr{BV}}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
for every $k\geq 0$.

\begin{definition}
\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.}
\end{definition}

\begin{definition}
\chris{The definition of the equivariant observables in a classical BV theory with a symmetry as the relative Chevalley Eilenberg complex with coefficients in local functionals, with its anti-bracket.}
\end{definition}

\begin{remark}
\chris{Remark on the d\'ecalage isomorphism with a reference, then give an interpretation of the relative Chevalley-Eilenberg complex after applying this isomorphism as the inclusion of background fields valued in the constant sheaf with value $\gg$.}
\end{remark}

\chris{mention smooth group actions, with a reference.}

@@

\begin{definition}
Let $(E, Q, \omega, I)$ be a classical field theory on $M$. The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
\[
\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
\]
\end{definition}

@@

\begin{definition}
A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{BRST} S_{BRST} = 0,\]
where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
\end{definition}

@@

The interacting theory is constructed as follows. First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$. These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
\] 
which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I_{\mr{BV}} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
\]

@@

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The {\bf generalized BF theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

@@

\item The BRST action is $S_{BRST} = 0$.
\end{itemize}
\end{definition}

@@

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The {\bf generalized Chern--Simons theory} is the following classical BV theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

@@

\item The interaction term is
\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
\end{itemize}
\label{def:generalizedBF}
\end{definition}

@@

\begin{definition}
A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
\end{definition}

@@

\begin{definition}
Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$. The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
\end{definition}

@@

\begin{definition}
A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
\end{definition}

@@

\chris{todo: replace the argument here with an argument that only works in terms of the $I^{(i)}$.}

@@

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.  Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.  We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.

\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
\chris{fix to take care with signs, also we're removing that earlier lemma so this all needs changing.}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
 &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\}.
\end{align*}
Here we applied Lemma \ref{onshell_action_lemma} on the third line.
\end{proof}

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand 
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + (123) \\
 &= \left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1)\right\rangle + (123),
\end{align*}
where $(123)$ indicates symmetrization in $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
\begin{align*}
\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= 
\end{align*}
\chris{...}

@@

\begin{definition}
A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
\end{definition}

@@

\begin{definition}
A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
\end{definition}

@@

\begin{definition}
Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

@@

In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are holomorphic.  They are stabilized by $\SU(4)$.  Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
 \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are topological.  They are stabilized by $\Spin(7) \sub \SO(8)$.  Again, twists by such supercharges can be made $\ZZ$-graded.
 \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
\end{enumerate}

@@

\begin{definition}
Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
For any open set $U \subset M$, define the following notations:
\begin{itemize}
\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
\end{itemize}
\end{definition}

@@

\begin{definition}\label{dfn: fnl}
Let $E$ be a vector bundle on $M$ and $U \subset M$.
The {\bf completed algebra of functions} on $\cE(U)$ is
\[
\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
\]
On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
\end{definition}

@@

\begin{definition} 
We use the following notations and naming conventions for sheaves on $\Mfld$:
\begin{itemize}
\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
\[
\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
\]
for every smooth manifold $X$, which is required to be natural under pullbacks:
\[
f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
\]
for every smooth map $f : X \to Y$. 
A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
\end{itemize}
\end{definition}

@@

\begin{definition}
Suppose $V,W$ are cochain complexes in convenient vector spaces. 
A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
\[
dif_c (f) : dif_c(V) \to dif_c(W)
\]
is a quasi-isomorphism of differentiable vector spaces.
\end{definition}
